The Asteroseismic Imprints of Mass Transfer

### 2024-04-11 paper/paper_AA.tex
Changes after referee report

\newcommand{\referee}[1]{{\bf #1}}

@@

The evolution of the donor (starting at D1) initially follows the 4$\,{\rm M_\odot}$ single star track, expanding across the main sequence, exhausting core hydrogen and moving across the Hertzsprung gap. During the expansion on the Hertzsprung gap, at point D2, the donor overflows its Roche-lobe and diverges from the single star track. As it loses mass, it is driven out of thermal equilibrium. It decreases in luminosity as a fraction of the photons produced deep inside are now used to do work to expand the outer layers.  The orbit shrinks slightly at first, but quickly starts to widen \citep{Renzo+2019:2019A&A...624A..66R}. At point D3 the donor star is still transferring mass but it starts to regain thermal equilibrium. At point D4 the donor has lost its entire hydrogen-rich envelope and contracts within its Roche-lobe. It keeps contracting until it ignites helium at the point marked D5, where it resides a compact subdwarf. \referee{As noted in Section~\ref{sec:model_setup}, we limit the accretion onto the companion to $0.5 \, {\rm M_\odot}$. Although the donor continues to transfer mass beyond this point, none of this mass is accreted by the companion and thus does not affect our accretor model. We mark this point on the donor's evolutionary track with a grey circle and highlight the rest of the track in grey.}

>>>>

% \newcommand{\referee}[1]{{\bf #1}}
\newcommand{\referee}[1]{{#1}}

@@

The evolution of the donor (starting at D1) initially follows the 4$\,{\rm M_\odot}$ single star track, expanding across the main sequence, exhausting core hydrogen and moving across the Hertzsprung gap. During the expansion on the Hertzsprung gap, at point D2, the donor overflows its Roche-lobe and diverges from the single star track. As it loses mass, it is driven out of thermal equilibrium. It decreases in luminosity as a fraction of the photons produced deep inside are now used to do work to expand the outer layers.  The orbit shrinks slightly at first, but quickly starts to widen \citep{Renzo+2019:2019A&A...624A..66R}. At point D3 the donor star is still transferring mass but it starts to regain thermal equilibrium. At point D4 the donor has lost its entire hydrogen-rich envelope and contracts within its Roche-lobe. It keeps contracting until it ignites helium at the point marked D5, where it resides a compact subdwarf. \referee{As noted in Section~\ref{sec:model_setup}, we limit the accretion onto the companion to $0.5 \, {\rm M_\odot}$. Although the donor continues to transfer mass beyond this point, none of this mass is accreted by the companion. We mark this point on the donor's evolutionary track with a grey circle and highlight subsequent evolution in grey.}
